---
title: "Class 12: Structural Bioinformatics Drug Discovery"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Clean up our protein target structure

First we download a target (i.e. protein receptor) structure from the main PDB database. We will pick PDB ID "1hsg"

```{r}
library(bio3d)

pdb.code <- "1hsg"
file.name <- get.pdb(pdb.code)
```

Extract the protein only segment of this PDB entry and write out a new PDB foramt file. We will also do the same for the bound ligand.

```{r}
hiv <- read.pdb(file.name)
hiv
```

Protein extraction first

```{r}
prot <- trim.pdb(hiv, "protein")
prot
```

```{r}
prot.filename <- paste(pdb.code, "_protein.pdb", sep="")
write.pdb(prot, file=prot.filename)
```

Do the same thing for ligand please...

```{r}
lig <- trim.pdb(hiv, "ligand")
write.pdb(lig, file=paste(pdb.code, "_ligand.pdb", sep="") )
```

```{r}
lig
```

## Convert out docking results for viewing in VMD

```{r}
res <- read.pdb("all.pdbqt", multi=TRUE)
res
```

```{r}
write.pdb(res, file="results.pdb")
```


### What is the RMSD to the MK1 compound from the crystal structure

```{r}
ori <- read.pdb("ligand.pdbqt")
rmsd(ori, res)
```

```{r}
rmsd(res)
```




